Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Fix typo
Add comment for @mkl
Add more on tests as documentation

Many Haskell programmers tend not to write test code even though the
strong type system of Haskell cannot always ensure correct semantics.
Without test code, it is difficult for users to understand usage of
functions and it is difficult for developers to maintain semantics
while extending software. To enhance the value of test code, we
propose to carry out behavior driven development with two tools:
doctest integrated with QuickCheck for user documentation and Hspec
with combinators extended for developer documentation. With our
method, specification can be used for documentation and automatic
testing. This kill-three-birds-with-one-stone aspect would motivate
Haskellers to write test code.

@@

Haskell programmers, however, is apt to rely on the type system too
much and tend not to write test code.  For example, the Haskell
Platform 2011.4.0.0 contains 23 packages (not counting the 19 core
libraries that come with GHC), but only 8 of them have a test suite (5
provide example code, 10 have no tests nor examples).  Lacking test
code also means that typical usage examples are not provided.

@@

\begin{quote}\begin{itemize}
    \item sol: Should we state that BDD-style TDD has been pioneered
        by RSpec?
\end{itemize}\end{quote}

@@

    sol: @kazu, can you work on this, if you have time.  I think an
    ``itemized'' list is better than text.  It more flexible for now,
    and @mkl or @sol can do the final wording)
\end{quote}

>>>>

Many Haskell programmers tend not to write test code even though the
strong type system of Haskell cannot always ensure correct semantics.
Test code helps users to understand the usage of
functions and developers to maintain semantics
while extending software. To ease the production and enhance the value of test code, we
propose to carry out behavior driven development with two tools:
doctest integrated with QuickCheck for user documentation and Hspec
with combinators extended for developer documentation. With our
method, specification can be used for documentation and automatic
testing. This kill-three-birds-with-one-stone aspect would motivate
Haskellers to write test code.

@@

Haskell programmers, however, is apt to rely on the type system too
much and tend not to write test code.  For example, the Haskell
Platform 2011.4.0.0 contains 23 packages (not counting the 19 core
libraries that come with GHC), but only 8 of them have a test suite (5
provide example code, 10 have no tests nor examples).
A lack of tests is not only a quality and maintainability issue.  It
is also a lack of documentation.  Tests document how code is supposed
to be used; and tests documents the behavior of code.

@@

\begin{quote}\begin{itemize}
    \item
        sol: Should we state that BDD-style TDD has been pioneered by
        RSpec?  By now I think it would be a good idea, that way it
        feels more natural to the reader that we always look at RSpec.

        @mkl: Where would that fit in?
\end{itemize}\end{quote}

@@

    sol: @kazu, can you work on this, if you have time.  I think an
    ``itemized'' list is better than text.  It's more flexible for
    now, and @mkl or @sol can do the final wording)
\end{quote}
